---
title: "R Project 1 - Hello R"
author: "Salman Salekin"
date: "1/28/2020"
output: 
  html_document:
    fig_height: 3
    fig_width: 4
    Theme: Modern
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen is a data frame with (142*13) = 1846 and 3 variables. The variables included in the data frame are:

+ __dataset__ : indicates which dataset the data from
+ __x__ : x-values
+ __y__ : y-values

```{r datasaurus_dozen}
datasaurus_dozen %>%
  count (dataset) %>%
  print (13)
```

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3



```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()
```

Calculating the correlation between 'x' and 'y' in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

### Exercise 4

Plotting the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + geom_point()
```

Now the correlation between 'x' and 'y' in the circle dataset is:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```

### Exercise 5

Finally, plot all dataset at once and calculate summary correlation coefficients.

```{r plot-all, fig.height=6, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + geom_point() + facet_wrap(~ dataset, ncol = 3) + theme(legend.position = "none")
```

```{r cor-a||}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x,y)) %>%
  print(13)
```




