---
title: "R Project 1 - Hello R"
author: "Michelle Pogue"
date: "Due Sept 8th"
output: 
  html_document: 
    fig_width: 12
    fig_height: 9
---

MAKE SURE YOU READ AND FOLLOW INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns(variables) included in the data frame. The variables are data set, x-values, and y-values.

```{r}
datasaurus_dozen %>%
count(dataset) %>%
print(23)
```

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 3

Let's plot the star data



```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

I'm some text, you should replace me with more meaningful text...
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

Plots of all data sets

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```