---
title: "R Project 1 - Hello R"
author: "Michelle Pogue"
date: "Due Sept 8th"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns(variables) included in the data frame. The variables are data set, x-values, and y-values.

```{r}
datasaurus_dozen %>%
count(dataset) %>%
print(13)
```

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 3

Let's plot the star data



```{r plot-star, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "stars")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

I'm some text, you should replace me with more meaningful text...
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
