---
title: "R Project 1 - Hello R"
author: "Rebecca Hinrichs"
date: "8 Sept 2021"
output: 
  html_document: 
    fig_width: 12
    fig_height: 12
    highlight: zenburn
    theme: simplex
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

A datasaurus_dozen file has 1846 rows and 3 variables:

dataset: indicates which dataset the data are from

x: x-values

y: y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=8, fig.width=8}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Next let's plot the data in the star dataset:

```{r plot-star, fig.height=8, fig.width=8}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Finally let's plot the data in the circle dataset:

```{r plot-circle, fig.height=8, fig.width=8}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

To finish it all off, let's plot all the data in the datasets:

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = "dataset"))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

And summarize the correlations between `x` and `y` in them:

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

